Programming Assignment 2

### 2015-04-02 paper.tex
Update paper.tex
Cant even
Wooordd

woorrdsss

%Feel free to remove the 'description' text i placed (e.g. "Our hopfield network was terrific! Type stuff here")
\section{Overview}

\section{Hopfield Autoassociative Memory Network}
The HAM network we constructed worked by creating large symmetric weight-matrices from image centroids (see Image Encoding subsection) to classify input vectors. The network is feed-back, meaning it feeds the resultant output vector back into itself as input until the network no longer exhibits any change on the vector.

>>>>

%Feel free to remove the 'description' text i placed (e.g. "Our hopfield network was terrific! Type stuff here")
\section{Overview}
This paper evaluates our results on various Neural Networks. These Neural
Networks were tested on standardized inputs and attempted to classify each
input appropriately. The performance of each Neural Network is determined by
the validity of their classifications. Each evaluation is discussed in more
detail in their appropriate sections.
\section{Hopfield Autoassociative Memory Network}
The HAM network we constructed worked by creating large symmetric weight-matrices from image centroids (see Image Encoding subsection) to classify input vectors. The network is feed-back, meaning it feeds the resultant output vector back into itself as input until the network no longer exhibits any change on the vector.
